Structural controllability of ecological networks

### 2018-06-26 paper/supp-info.Rmd
Caption table supp info was incorrect
Remove prob. superior from supp info
Close #24

c_mod_table %>% 
  dplyr::mutate(weight = round(weight, 2)) %>%
  knitr::kable("latex", 
               escape = FALSE, 
               booktabs = TRUE, 
               digits = 2, 
               linesep = c(""),
               caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks. There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (c), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$). Only candidate models with $\\Delta AIC < 8$ are shown.") %>%
  kableExtra::kable_styling(font_size = 8)
```

```{r tab-species-model-random, warning=FALSE}
drake::loadd(species_model_cc, species_model_superior)

@@

tab_cc %>%
  dplyr::bind_rows(tab_su) %>%
  dplyr::mutate(random = pretty_term_names(random)) %>%
  dplyr::rename(`random effects` = random) %>%
  knitr::kable("latex", 
               booktabs = T, 
               caption = "Selection table of the random effects in the generalised mixed effect models of control capacity $\\phi$ and the probability of being a superior node $\\sigma$. Only models with a weight larger than 0.01 are shown. We modelled the probability of being a superior node without random effects as the random intercept over site had zero variance.", 
               row.names = F, 
               digits = 2, 
               escape = F) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::group_rows("control capacity models", 1, nrow(tab_cc)) %>%
  kableExtra::group_rows("superior probability models", nrow(tab_cc) + 1, nrow(tab_cc) + nrow(tab_su)) 
```

```{r tab-model-output-species-level}
best_model_cc <- species_model_cc %$%
  fixed %>%
  get_best_model() 
best_model_su <- species_model_superior %$%
  fixed %>%
  get_best_model()

num_effects <- get_num_effects(best_model_cc)

table_df <- best_model_cc %>%
  broom::tidy() %>%
  dplyr::bind_rows(broom::tidy(best_model_su))

table_df %>%
  dplyr::mutate(group = dplyr::if_else(is.na(group), "fixed", group)) %>%
  dplyr::select(group, term, estimate, std.error, statistic, p.value) %>%
  dplyr::mutate(term = pretty_term_names(term)) %>%
  knitr::kable("latex", 
               col.names = c("effect type", "term", "estimate", "std. error", "z value", "p value"),
               booktabs = T, 
               caption = "Summary table of the control capacity model with the smallest AICc.", 
               row.names = F, 
               digits = 2, 
               escape = F) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::group_rows("control capacity models", 1, purrr::reduce(num_effects, sum)) %>%
  kableExtra::group_rows("superior probability models", purrr::reduce(num_effects, sum) + 1, nrow(table_df))

@@

```{r tab-var-importance}
cc_imp <- get_var_importance(species_model_cc$fixed) 
su_imp <- get_var_importance(species_model_superior$fixed)

dplyr::bind_rows(cc_imp, su_imp) %>%
  dplyr::mutate(term = pretty_term_names(term)) %>%
  knitr::kable("latex", 
               booktabs = T, 
               row.names = F, 
               digits = 2, 
               escape = F, 
               caption = "Variable importance for each set of models. The importance is the sum of the weights of all models in which the variable was included.",
               linesep = '') %>%
  kableExtra::kable_styling(font_size = 8)%>%
  kableExtra::group_rows("control capacity models", 1, nrow(cc_imp)) %>%
  kableExtra::group_rows("superior probability models", nrow(cc_imp) + 1, nrow(cc_imp) + nrow(su_imp))
```

```{r fig-superior, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap = "Relationship between the most important variables in the models of superior probability. The plots show the values predicted by most parsimonious model. Invasive species are depicted with solid orange circles."}
drake::loadd(fig_superior)
cowplot::plot_grid(plotlist = fig_superior, ncol = 2)
```

```{r fig-species-models-degree, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap = "Relationship between degree and (a) the control capacity and (b) the probability of being a superior node. The plots show the values predicted by most parsimonious model for each response variable. The invasive species are depicted with solid orange circles."}
drake::loadd(fig_models_degree)
library(ggplot2)
fig_models_degree %<>% add_internal_margins()
cowplot::plot_grid(plotlist = fig_models_degree, ncol = 2)
```

>>>>

c_mod_table %>% 
  dplyr::mutate(weight = round(weight, 2)) %>%
  knitr::kable("latex", 
               escape = FALSE, 
               booktabs = TRUE, 
               digits = 2, 
               linesep = c(""),
               caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks. There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (c), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$). Only candidate models with a weight $>0.01$ are shown.") %>%
  kableExtra::kable_styling(font_size = 8)
```

```{r tab-species-model-random, warning=FALSE, eval = F}
drake::loadd(species_model_cc, species_model_superior)

@@

tab_cc %>%
  dplyr::bind_rows(tab_su) %>%
  dplyr::mutate(random = pretty_term_names(random)) %>%
  dplyr::rename(`random effects` = random) %>%
  knitr::kable("latex", 
               booktabs = T, 
               caption = "Selection table of the random effects in the generalised mixed effect models of control capacity $\\phi$ and the probability of being a superior node $\\sigma$. Only models with a weight larger than 0.01 are shown. We modelled the probability of being a superior node without random effects as the random intercept over site had zero variance.", 
               row.names = F, 
               digits = 2, 
               escape = F) %>%
  kableExtra::kable_styling(font_size = 8) #%>%
  # kableExtra::group_rows("control capacity models", 1, nrow(tab_cc)) %>%
  # kableExtra::group_rows("superior probability models", nrow(tab_cc) + 1, nrow(tab_cc) + nrow(tab_su)) 
```

```{r tab-model-output-species-level}
drake::loadd(species_model_cc)

best_model_cc <- species_model_cc %$%
  fixed %>%
  get_best_model() 
# best_model_su <- species_model_superior %$%
  # fixed %>%
  # get_best_model()

# num_effects <- get_num_effects(best_model_cc)

table_df <- best_model_cc %>%
  broom::tidy()# %>%
  # dplyr::bind_rows(broom::tidy(best_model_su))

table_df %>%
  # dplyr::mutate(group = dplyr::if_else(is.na(group), "fixed", group)) %>%
  dplyr::select(term, estimate, std.error, statistic, p.value) %>%
  dplyr::mutate(term = pretty_term_names(term)) %>% 
  knitr::kable("latex", 
               # col.names = c("effect type", "term", "estimate", "std. error", "z value", "p value"),
               booktabs = T, 
               caption = "Summary table of the control capacity model with the smallest AICc.", 
               row.names = F, 
               digits = 2, 
               escape = F) %>%
  kableExtra::kable_styling(font_size = 8)# %>%
  # kableExtra::group_rows("control capacity# models", 1, purrr::reduce(num_effects, sum)) %>%
  # kableExtra::group_rows("superior probability models", purrr::reduce(num_effects, sum) + 1, nrow(table_df))

@@

```{r tab-var-importance}
cc_imp <- get_var_importance(species_model_cc$fixed) 
# su_imp <- get_var_importance(species_model_superior$fixed)

# dplyr::bind_rows(cc_imp, su_imp) %>%
  cc_imp %>%
  dplyr::mutate(term = pretty_term_names(term)) %>%
  knitr::kable("latex", 
               booktabs = T, 
               row.names = F, 
               digits = 2, 
               escape = F, 
               caption = "Variable importance for control capacity models. The importance is the sum of the weights of all models in which the variable was included.",
               linesep = '') %>%
  kableExtra::kable_styling(font_size = 8) #%>%
  # kableExtra::group_rows("control capacity models", 1, nrow(cc_imp)) %>%
  # kableExtra::group_rows("superior probability models", nrow(cc_imp) + 1, nrow(cc_imp) + nrow(su_imp))
```

```{r fig-superior, eval = FALSE, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap = "Relationship between the most important variables in the models of superior probability. The plots show the values predicted by most parsimonious model. Invasive species are depicted with solid orange circles."}
drake::loadd(fig_superior)
cowplot::plot_grid(plotlist = fig_superior, ncol = 2)
```

```{r fig-species-models-degree, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap = "Relationship between degree and (a) control capacity and (b) the probability of being a superior node."}
drake::loadd(fig_models_degree)
library(ggplot2)
# fig_models_degree %<>% add_internal_margins()
fig_models_degree  %>%
  purrr::map(function(x) x + theme(plot.margin = grid::unit(c(1.5, 0.5, 1.5, 0.5), "mm"))) %>%
  cowplot::plot_grid(plotlist = ., ncol = 1)
# fig_models_degree[[1]]
```
